Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-02 paper/figures.tex

\nextgroupplot[
	title=B1(b) Top organizations (http-www),
	allDatasetsMultiYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsMultiYbarPart2,
	bar width=2.5pt,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
]

@@

\nextgroupplot[
	title=B2(b) Top organizations (http-www),
	allDatasetsMultiYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsMultiYbarPart2,
	bar width=2.5pt,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
]

@@

\tikzsetnextfilename{mini-2x2-secure-response-redirect-ybar}
\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 2,
		horizontal sep=8pt,
		vertical sep=16pt,
	},
]
\nextgroupplot[
	title=B1(c) Resp./redir. sec. (https-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpsWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mix sec}{3xx Mixed}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Insec}{3xx Insecure}{red}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww;
\addlegendentry{3xx Final redirect secure}

@@

\nextgroupplot[
	title=B2(c) Resp./redir. sec. (https-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpsWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mix sec}{3xx Mixed}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Insec}{3xx Insecure}{red}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww;
\addlegendentry{3xx Final redirect secure}

\nextgroupplot[
	title=B1(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mix sec}{3xx Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Insec}{3xx Insecure}{orange}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww;
\addlegendentry{3xx Final redirect secure}

@@

\nextgroupplot[
	title=B2(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Sec}{3xx Secure}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mix sec}{3xx Mixed}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Insec}{3xx Insecure}{orange}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww;
\addlegendentry{3xx Final redirect secure}

@@

	\nextgroupplot[
		title=C1 Sweden,
		xlabel=http-www,
		ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedSwedenHttpHttpsWww

@@

	\nextgroupplot[
		title=C2 Global,
		xlabel=http-www,
		% ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
		yticklabels={},
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedGlobalHttpHttpsWww

>>>>

\nextgroupplot[
	title=B1(b) Top organizations (http-www),
	allDatasetsMultiYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsMultiYbarPart2,
	bar width=2.5pt,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\nextgroupplot[
	title=B2(b) Top organizations (http-www),
	allDatasetsMultiYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsMultiYbarPart2,
	bar width=2.5pt,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\tikzsetnextfilename{mini-2x2-secure-response-redirect-ybar}
\begin{tikzpicture}
\begin{groupplot}[
	group style={
		group size=2 by 2,
		horizontal sep=8pt,
		vertical sep=8pt,
	},
]
\nextgroupplot[
	% title=B1(c) Resp./redir. sec. (https-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpsWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Insec}{3xx Insec}{red}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww;
\addlegendentry{3xx Final sec}

@@

\nextgroupplot[
	% title=B2(c) Resp./redir. sec. (https-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpsWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Insec}{3xx Insec}{red}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww;
\addlegendentry{3xx Final sec}

\nextgroupplot[
	% title=B1(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	swedenHttpWwwDatasetsYbar,
	width=.55\textwidth,
	xticklabels={Counties,Domain registrars,Financial services,GOCS,Higher education,ISPs,Media,Municipalities,Public authorities,reach50,Top 10k .se,Rand 100k .se,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Insec}{3xx Insec}{orange}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww;
\addlegendentry{3xx Final sec}

@@

\nextgroupplot[
	% title=B2(d) Resp./redir. sec. (http-www),
	allDatasetsStackedYbar,
	allDatasetsYbar,
	allDatasetsYbarMiniResults,
	allDatasetsStackedYbarPart2,
	globalHttpWwwDatasetsYbar,
	width=.4\textwidth,
	yticklabels={},
	xticklabels={Top 10k .se,Top 10k .dk,Top 10k global,Rand 100k .se,Rand 10k .dk,Rand 10k .com,Rand 10k .net,Rand 10k global,},
	xticklabel style={
		rotate=45,
		anchor={north east},
	},
]

@@

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Insec}{3xx Insec}{orange}{}

@@

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww;
\addlegendentry{3xx Final sec}

@@

	\nextgroupplot[
		% title=C1 Sweden,
		xlabel=http-www,
		ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedSwedenHttpHttpsWww

@@

	\nextgroupplot[
		% title=C2 Global,
		xlabel=http-www,
		% ylabel=https-www,
		allDatasetsScatter,
		allDatasetsScatterMiniResults,
		scatter/classes={
			Any={mark=square*,blue},%
			Disconnect={mark=triangle*,red},%
			Content={mark=x,draw=black},%
			Advertising={mark=o,draw=red},%
			Analytics={mark=diamond,draw=blue},%
			Social={mark=+,draw=green}%
		},%
		yticklabels={},
	]
	\addDefaultScatterTableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedGlobalHttpHttpsWww
